POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2022-01-25 main.tex
add figure to start planning the concrete benchmark

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{images/benchmark.jpeg}
  \caption{The benchmark's big picture.}
  \label{fig:bigpic}
\end{figure}

The big picture for the benchmark can be seen in \cref{fig:bigpic}
where the three pillars (i.e.: concepts typically needed for process
calculus proofs) appear in blue, with some ideas of what to prove. And
a second step of combining the three aspects (for a total of six steps
for the whole benchmark), and of course the $+1$-step for the
combination of everything on the reader's next research papers.
